---
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup-197379, eval = F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
source('scripts/packages.R')
source('scripts/tables.R')

```

```{r  load-data-197379}
my_site <- 197379

```

`r fpr::fpr_appendix_title()`

## Site Location {.unnumbered}

PSCIS crossing `r as.character(my_site)` is located on
`r fpr::fpr_my_pscis_info()` approximately 5km west of the town of
Smithers. PSCIS crossing `r as.character(my_site)` is located on
`r fpr_my_pscis_info(col_pull = road_name)`. Crossing
`r as.character(my_site)` was located
`r round(fpr::fpr_my_bcfishpass(col_pull = downstream_route_measure)*0.001, 1)`km
upstream from the confluence with the Zymoetz River and is the
responsibility of the Ministry of Transportation and Infrastructure.

<br>

## Background {.unnumbered}

At crossing `r as.character(my_site)`, `r fpr::fpr_my_pscis_info()` is a
`r fpr::fpr_my_bcfishpass() %>% english::ordinal()` order stream with a
watershed area upstream of the crossing of approximately
`r fpr::fpr_my_wshd()`km^2^. The elevation of the watershed ranges from
a maximum of `r fpr::fpr_my_wshd(col = 'elev_max')`m to
`r fpr::fpr_my_wshd(col = 'elev_site')`m at the crossing (Table
\@ref(tab:tab-wshd-197379)). Upstream of crossing
`r as.character(my_site)`, `r fpr::fpr_my_fish_sp()` have previously
been recorded [@moe2020KnownBC; @norris2020bcfishobs].

<br>

```{r tab-wshd-197379, eval = T}
fpr::fpr_table_wshd_sum(site_id = my_site) %>% 
  select(-'Elev Min') %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of derived upstream watershed statistics for PSCIS crossing ', my_site, '.'),
           footnote_text = 'Elev P60 = Elevation at which 60% of the watershed area is above',
           scroll = F)

```

<br>

PSCIS stream crossing `r as.character(my_site)` was ranked as a high
priority for follow up by the Society for Ecosystem Restoration in
Northern BC because of
significant amounts of habitat modelled upstream of the crossing. A summary of habitat modelling outputs is
presented in Table \@ref(tab:tab-culvert-bcfp-197379). A map of the
watershed is provided in map attachment
[`r fpr::fpr_my_bcfishpass(col_pull = dbm_mof_50k_grid)`](fpr::fpr_my_mapsheet()).

`r if(identical(gitbook_on, FALSE)){knitr::asis_output("\\pagebreak")}`

<br>

```{r tab-culvert-bcfp-197379, eval = T}
fpr::fpr_table_bcfp(scroll = gitbook_on) 
```

<br>

## Aerial Imagery {.unnumbered}

Surveys were conducted with a remotely piloted aircraft at the crossing with resulting images stitched into an orthomosaic and 3-dimensional model. 

<br>

## Fish Sampling {.unnumbered}

Electrofishing was conducted with results summarised in Tables
\@ref(tab:tab-fish-site-197379) - \@ref(tab:tab-fish-dens-197379) and Figure
\@ref(fig:plot-fish-box-197379).

<br>

## Conclusion {.unnumbered}

There was
`r fpr::fpr_my_priority_info(col_pull= upstream_habitat_length_km)`km of
habitat modelled upstream of crossing `r as.character(my_site)` with
areas surveyed rated as
`r fpr::fpr_my_priority_info(sit = my_site, loc = 'us', col_pull = hab_value)`
value for salmonid rearing and spawning. Crossing
`r as.character(my_site)` was ranked as a
`r fpr::fpr_my_priority_info(col_pull = priority)` priority for
proceeding to design for replacement. Sandstone Creek is a
large system with habitat suitable for numerous species including cutthroat
and dolly varden. Development of a plan to replace the crossing with
a bridge would be a key step in eliminating an outlet drop and reducing
flow velocities at the highway crossing.

`r if(gitbook_on){knitr::asis_output("<br>")} else knitr::asis_output("\\pagebreak")`

<br>

```{r tab-habitat-summary-197379}
tab_hab_summary %>% 
  filter(Site  == my_site) %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of habitat details for PSCIS crossing ', my_site, '.'),
                 scroll = F) 

```

<br>

```{r tab-fish-site-197379, eval=T}
fpr_table_fish_site()

```

<br>

```{r tab-fish-dens-197379, eval=T}
fpr_table_fish_density()

```

`r if(gitbook_on){knitr::asis_output("<br>")} else knitr::asis_output("\\pagebreak")`

```{r plot-fish-box-197379, fig.cap= my_caption, eval=T}
my_caption <- paste0('Densites of fish (fish/100m2) captured upstream of PSCIS crossing ', my_site, '.')

fpr_plot_fish_box() 

```
